Stable Neo-Hookean Flesh Simulation

### 2019-09-30 LaTeX-Master-Vorlage/chapter/Background.tex
fixed literaturverzeichnis, added todo package, fixed some warnings

\[
\mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right]=\boldsymbol{\check{A}}
\]

@@

\begin{addmargin}[2cm]{2cm}
a: scalar \\
\textbf{A}: matrix or tensor \\
\textbf{a}: vector \\
vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix \\
\end{addmargin}

@@

Measure for the deformation, length and volume change etc.
Nonlinear deformations
http://www.continuummechanics.org/deformationgradient.html
also add some examples

>>>>

\[
\mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
\]

This term is equivalent to the following notation:

\[
\mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
=\boldsymbol{\check{A}}
\]

@@

\begin{addmargin}[2cm]{2cm}
a: scalar \\
\textbf{A}: matrix or tensor \\
\textbf{a}: vector \\
vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix
\end{addmargin}

@@

\todoredefined[inline]{
TODO: Include measure for the deformation, length and volume change etc. \\
Nonlinear deformations: \\
http://www.continuummechanics.org/deformationgradient.html
\\ also add some examples
}

### 2019-09-30 LaTeX-Master-Vorlage/main.tex
fixed literaturverzeichnis, added todo package, fixed some warnings

\printbibliography[heading=bibintoc, keyword={book}, title={Literaturverzeichnis}]\clearpage
\printbibliography[heading=bibintoc, keyword={online}, title={Onlinequellen}]\clearpage
\printbibliography[heading=bibintoc, keyword={image}, title={Bildquellen}]\clearpage

>>>>

% trying to make bibliography work
\defbibfilter{booksAndPapers}{
  type=article or
  type=inproceedings or
  type=incollection or
  type=book or
  type=inbook or
  type=misc
}
\defbibfilter{onlineSource}{
  type=online
}

\printbibliography[heading=bibintoc, filter=booksAndPapers, title={Bibliography}]\clearpage
\printbibliography[heading=bibintoc, filter=onlineSource, title={Online Sources}]\clearpage
\printbibliography[heading=bibintoc, keyword={image}, title={Figure Sources}]\clearpage

%\printbibliography[heading=bibintoc, keyword={book}, title={Literature}]\clearpage
%\printbibliography[heading=bibintoc, keyword={article}, title={Articles}]\clearpage
%\printbibliography[heading=bibintoc, keyword={online}, title={Online Resources}]\clearpage
%\printbibliography[heading=bibintoc, type=misc,title={Various References}] \clearpage
%\printbibliography[heading=bibintoc, keyword={image}, title={Images Resources}]\clearpage
